---
title: "p8105_hw6_jn2761"
author: "jiaying Ning"
date: "11/30/2020"
output: html_document
---

load packages
```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
library(modelr)
library(mgcv)
library(readxl)
library(janitor)


knitr::opts_chunk$set(
  fig.width = 6,
    fig.asp = .6,
  out.width = "90%"

)

theme_set(theme_minimal()+theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_color_discrete = scale_color_viridis_d
scale_fill_discrete =scale_fill_viridis_d
```

## Problem 1

### Import data
```{r}
birthweight_df = read_csv("./data/birthweight.csv") %>%
  na.omit() 


  
  
```
```{r}
birthweight_df %>%
  summary()
```

From description of variable, we know that variable`babysex`, `frace`,`malform`,`mrace` should be factor
```{r}
birthweight_df=
birthweight_df %>%
   mutate(babysex = ifelse(babysex == 1, "male","female"),
     malform = ifelse(malform == 0, "absent","present"),
          frace = recode(frace, `1` = "White", `2`="Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other", `9` = "Unknown"),
          mrace = recode(mrace, `1` = "White", `2`="Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other"))
```


### Propose a regression model for birthweight

In order to find the variable of interest, I did research on the potential risk factor that influence newborn's birthwright, and here is what I found:

- *The present study revealed that* ***maternal illiteracy, exposure to passive smoking, late child bearing, shorter inter-pregnancy interval, previous LBW baby, maternal weight, weight gain during pregnancy, PIH, high risk pregnancy and late antenatal registration*** *were the risk factors significantly associated with the birth weight of a newborn(Metgud,2012)* 
- [Click Here to see the original paper](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3390317/#)

For the current homework, I will choose variable`gaweeks`(as measurement for inter-pregnancy interval) and `momage`(as measurement for late child bearing)as my predictor, and `bwt` as my outcome.



```{r}
birthweight_df %>%
  ggplot(aes(x=gaweeks,y=bwt,color=smoken))+
  geom_point(alpha=0.5) +
  facet_grid(.~babysex)

birthweight_df %>%
  ggplot(aes(x=momage,y=bwt,color=smoken))+
  geom_point(alpha=0.5) 
```

Fit in a linear model:
```{r}
Lin_mod = lm(bwt ~ momage + gaweeks, data = birthweight_df)
broom::tidy(Lin_mod)


```

### plot of model residuals against fitted value
```{r}

library(patchwork)

momage_res=
modelr::add_residuals(birthweight_df, Lin_mod) %>%
  ggplot(aes(x=momage,y=resid))+
   geom_point() 

gaweeks_res=
modelr::add_residuals(birthweight_df, Lin_mod) %>%
  ggplot(aes(x=gaweeks,y=resid))+
   geom_point() 

momage_res+gaweeks_res
```

### Comparing with two other model

#### 1. length at birth and gestational age as predictors (main effects only)

```{r}

mod1 = lm(bwt ~ blength + gaweeks, data = birthweight_df)

```


#### 2. head circumference, length, sex, and all interactions (including the three-way interaction) 

```{r}

mod2 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = birthweight_df)

```

#### Compare

```{r}
cv_df=
  crossv_mc(birthweight_df,100) %>%
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) %>% 
  mutate(
    mod0  = map(train, ~lm(bwt ~ momage + gaweeks, data = .x)),
    mod1  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    mod2  = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x))) %>% 
  mutate(
    rmse_mod0 = map2_dbl(mod0, test, ~rmse(model = .x, data = .y)),
    rmse_mod1 = map2_dbl(mod1, test, ~rmse(model = .x, data = .y)),
    rmse_mod2 = map2_dbl(mod2, test, ~rmse(model = .x, data = .y)))
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```


```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>%
  group_by(model) %>%
  summarize(avg_rmse = mean(rmse))
```


In here we see that model 2 (head circumference, length, sex, and all interactions) have the smallest root mean squared errors, thus provide the best model for predicting birthweight


## Problem 3

### Import data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

### Bootstrapping 

95% confidence interval for r̂ 2 

```{r}
weather_bootstrap=
weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~ lm(tmax ~ tmin, data = .x)))

```


- 95% confidence interval for r̂ 2 


```{r}
weather_bootstrap%>%
  mutate(
    results = map(models, broom::glance)) %>% 
  select(results) %>% 
  unnest(results) %>%
  summarise(
    ci_lower=quantile(r.squared,0.025),
    ci_upper=quantile(r.squared,0.975)
  )
```


- 95% confidence interval for log(β̂ 0∗β̂ 1)


```{r}
weather_bootstrap%>%
   mutate(
    results = map(models, broom::tidy))
```
```{r}
weather_bootstrap%>%
   mutate(
    results = map(models, broom::tidy))%>% 
  select(results,.id) %>% 
  unnest(results) 
```


```{r}

weather_bootstrap%>%
   mutate(
    results = map(models, broom::tidy))%>% 
  select(results,.id) %>% 
  unnest(results)  %>%
  select(term,estimate,.id)%>%
  pivot_wider(
  names_from = "term",  
  values_from = "estimate")%>%
  unnest() 
```


```{r}
a=weather_bootstrap%>%
   mutate(
    results = map(models, broom::tidy))%>% 
  select(results,.id) %>% 
  unnest(results)  %>%
  select(term,estimate,.id)%>%
  pivot_wider(
  names_from = "term",  
  values_from = "estimate")%>%
  unnest()
```

```{r}
a %>%
  mutate( log = log(`(Intercept)`*tmin)) %>%
  summarise(
    ci_lower=quantile(log,0.025),
    ci_upper=quantile(log,0.975)
  )
        
```
