---
title: "p8105_hw6_jn2761"
author: "jiaying Ning"
date: "11/30/2020"
output: html_document
---

load packages
```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
library(modelr)
library(mgcv)
library(readxl)
library(janitor)


knitr::opts_chunk$set(
  fig.width = 6,
    fig.asp = .6,
  out.width = "90%"

)

theme_set(theme_minimal()+theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_color_discrete = scale_color_viridis_d
scale_fill_discrete =scale_fill_viridis_d
```

## Problem 1

### Import data
```{r}
birthweight_df = read_csv("./data/birthweight.csv") %>%
  na.omit() 


  
  
```
```{r}
birthweight_df %>%
  summary()
```

From description of variable, we know that variable`babysex`, `frace`,`malform`,`mrace` should be factor
```{r}
birthweight_df=
birthweight_df %>%
   mutate(babysex = ifelse(babysex == 1, "male","female"),
     malform = ifelse(malform == 0, "absent","present"),
          frace = recode(frace, `1` = "White", `2`="Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other", `9` = "Unknown"),
          mrace = recode(mrace, `1` = "White", `2`="Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other"))
```


### Propose a regression model for birthweight

In order to find the variable of interest, I did research on the potential risk factor that influence newborn's birthwright, and here is what I found:

- *The present study revealed that* ***maternal illiteracy, exposure to passive smoking, late child bearing, shorter inter-pregnancy interval, previous LBW baby, maternal weight, weight gain during pregnancy, PIH, high risk pregnancy and late antenatal registration*** *were the risk factors significantly associated with the birth weight of a newborn(Metgud,2012)* 
- [Click Here to see the original paper](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3390317/#)

For the current homework, I will choose variable`gaweeks`(as measurement for inter-pregnancy interval) and `momage`(as measurement for late child bearing)as my predictor, and `bwt` as my outcome.



```{r}
birthweight_df %>%
  ggplot(aes(x=gaweeks,y=bwt,color=smoken))+
  geom_point(alpha=0.5) +
  facet_grid(.~babysex)

birthweight_df %>%
  ggplot(aes(x=momage,y=bwt,color=smoken))+
  geom_point(alpha=0.5) 
```

Fit in a linear model:
```{r}
Lin_mod = lm(bwt ~ momage + gaweeks, data = birthweight_df)
broom::tidy(Lin_mod)


```

### plot of model residuals against fitted value
```{r}

library(patchwork)

momage_res=
modelr::add_residuals(birthweight_df, Lin_mod) %>%
  ggplot(aes(x=momage,y=resid))+
   geom_point() 

gaweeks_res=
modelr::add_residuals(birthweight_df, Lin_mod) %>%
  ggplot(aes(x=gaweeks,y=resid))+
   geom_point() 

momage_res+gaweeks_res
```

### Comparing with two other model

